Model Checking

### 2023-05-27 owen/Write Ups/03_existing_models.qmd
finish off the write up

```{r plot some parts of this model}

@@

Comparing the predictive performance of the model from 
the slides (**without covariates**) it is unsurprisingly 
not comparable to the current iteration of the model we have here.

>>>>

```{r plot some parts of this model}
#| fig-height: 8

@@

fit_ppt <- readRDS(here("owen", "cluster_scripts", "Cluster_stan_ppt_2_n10.RDS"))

focal <- paste0("beta[", c(1, 127, 1207, 1263, 1519, 1635, 
                           1789, 2084, 2139, 2441, 2503, 2561, 
                           2679, 2707, 2781, 2836, 3533, 3714), "]")

mcmc_hist(fit_ppt$draws(focal))

focal_gamma <- paste0("gamma[", c(1, 127, 1207, 1263, 1519, 1635, 
                           1789, 2084, 2139, 2441, 2503, 2561, 
                           2679, 2707, 2781, 2836, 3533, 3714), "]")

mcmc_hist(fit_ppt$draws(focal_gamma))
```

![Predictive Checks](../cluster_scripts/ppd_model2.png)

This model gives similar predictive performance to the previously proposed
model.
